Hybrid platforms and bargaining power

### 2022-12-16 src/paper/application.tex
Minor structure enhancements

Additionally, customers can also choose from a unit mass of outside options, yielding utility $u^0_ij = \mu\epsilon^0_{ij}$

$\epsilon^F_{ij}$ and $\epsilon^0_{ij}$ are assumed to be independent and identically distributed (i.i.d.) across consumers and products, and follow a standardized Type I Extreme Value distribution. This distributional assumption, along with the fact that each consumer consumes only one product, will lead to a tractable, logit-form demand function.

@@

The game starts by the platform announcing its entry fee $F_F$.
Next, each fringe firm decides whether to create a product at cost $I_F$ and enter the market.
After that, the firms that have made the investment decide if they also want to enter the platform for the announced fee $F_F$.\footnote{
    In the benchmark model, separating these two decisions is redundant, as, in any subgame perfect equilibrium, any firm that makes the investment will also enter the platform.
    However, in the model with bargaining, this distinction is crucial.
}
Finally, the platform and the fringe firms simultaneously choose the prices for their products.
Each consumer then chooses the one maximizing their utility, and profits are realized.

@@

The main difference between the benchmark and the bargaining model is in determining the entry fee $F_F$.
In the former, the platform unilaterally sets the fee, and the fringe treats it as a take it or leave it offer.
On the other hand, in the bargaining model, I assume that the entry fee is the result of a negotiation between the platform and those firms that have made the investment.
% TODO: entry fee cap?

@@

\subsection{Fringe entry}

>>>>

Additionally, customers can also choose from a unit mass of outside options, yielding utility $u^0_ij = \mu\epsilon^0_{ij}$. $\epsilon^F_{ij}$ and $\epsilon^0_{ij}$ are assumed to be independent and identically distributed (i.i.d.) across consumers and products, and follow a standardized Type I Extreme Value distribution. This distributional assumption, along with the fact that each consumer consumes only one product, will lead to a tractable, logit-form demand function.

@@

In the benchmark model, the game starts by the platform announcing its entry fee $F_F$.
In the bargaining case, the platform cannot commit to entry fees, so this step is skipped.
Next, each fringe firm decides whether to create a product at cost $I_F$ and enter the market.
In the bargaining model, the entry fee is decided at this point, as a result of a negotiation between the platform and the firms that have made the investment.
After that, the firms that have made the investment decide if they also want to enter the platform for the announced fee $F_F$.\footnote{
    In the benchmark model, separating these two decisions is redundant, as, in any subgame perfect equilibrium, any firm that makes the investment will also enter the platform.
    However, in the model with bargaining, this distinction is crucial.
}
Finally, the platform and the fringe firms simultaneously choose the prices for their products.
Each consumer then chooses the one maximizing their utility, and profits are realized.

@@

The main difference between the benchmark and the bargaining model is in determining the entry fee $F_F$.
In the former, the platform unilaterally sets the fee, and the fringe treats it as a take it or leave it offer.
On the other hand, in the bargaining model, I assume that the entry fee is the result of a negotiation between the parties.
% TODO: entry fee cap?

@@
